### 2022-09-21 dissertation/chapters/08-results.tex
✨ (review): Adding data and analysis

\begin{figure}[htbp]
    \begin{subfigure}{0.49\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/train_loss.png}
        \caption{Train loss}
        \label{fig:results:case_study:iris:train:loss}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/test_loss.png}
        \caption{Test loss}
        \label{fig:results:case_study:iris:test:loss}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{0.49\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/train_accuracy.png}
        \caption{Train accuracy}
        \label{fig:results:case_study:iris:train:accuracy}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/test_accuracy.png}
        \caption{Test accuracy}
        \label{fig:results:case_study:iris:test:accuracy}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{\textwidth}
    	\centering
        \includegraphics[width=0.35\textwidth]{analysis/bhh_case_study/iris/legend.png}
        \caption{Legend}
        \label{fig:results:case_study:iris:legend}
    \end{subfigure}
    \par\bigskip
    \caption{Train and test behaviour of the \Ac{BHH} baseline for different configurations of replay window size}
    \label{fig:results:case_study:iris:metric_plots}
\end{figure}

@@

\begin{figure}[htbp]
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[0].png}
        \caption{$\alpha_{0}$ - \Acs{SGD}}
        \label{fig:results:case_study:iris:alpha:0}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[1].png}
        \caption{$\alpha_{1}$ - \Acs{Momentum}}
        \label{fig:results:case_study:iris:alpha:1}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[2].png}
        \caption{$\alpha_{2}$ - \Acs{NAG}}
        \label{fig:results:case_study:iris:alpha:2}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[3].png}
        \caption{$\alpha_{3}$ - \Acs{Adagrad}}
        \label{fig:results:case_study:iris:alpha:3}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[4].png}
        \caption{$\alpha_{4}$ - \Acs{RMSProp}}
        \label{fig:results:case_study:iris:alpha:4}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[5].png}
        \caption{$\alpha_{5}$ - \Acs{Adadelta}}
        \label{fig:results:case_study:iris:alpha:5}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[6].png}
        \caption{$\alpha_{6}$ - \Acs{Adam}}
        \label{fig:results:case_study:iris:alpha:6}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[7].png}
        \caption{$\alpha_{7}$ - \Acs{PSO}}
        \label{fig:results:case_study:iris:alpha:7}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[8].png}
        \caption{$\alpha_{8}$ - \Acs{GA}}
        \label{fig:results:case_study:iris:alpha:8}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/alpha[9].png}
        \caption{$\alpha_{9}$ - \Acs{DE}}
        \label{fig:results:case_study:iris:alpha:9}
    \end{subfigure}
    \par\bigskip
    \caption{Change in the concentration of $\alpha$ during training for various heuristics}
    \label{fig:results:case_study:iris:alpha}
\end{figure}

@@

\begin{figure}[htbp]
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[0].png}
        \caption{$P(\theta_{0} | \alpha)$ - \Acs{SGD}}
        \label{fig:results:case_study:iris:p_theta:0}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[1].png}
        \caption{$P(\theta_{1} | \alpha)$ - \Acs{Momentum}}
        \label{fig:results:case_study:iris:p_theta:1}
    \end{subfigure}
    \par\medskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[2].png}
        \caption{$P(\theta_{2} | \alpha)$ - \Acs{NAG}}
        \label{fig:results:case_study:iris:p_theta:2}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[3].png}
        \caption{$P(\theta_{3} | \alpha)$ - \Acs{Adagrad}}
        \label{fig:results:case_study:iris:p_theta:3}
    \end{subfigure}
    \par\medskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[4].png}
        \caption{$P(\theta_{4} | \alpha)$ - \Acs{RMSProp}}
        \label{fig:results:case_study:iris:p_theta:4}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[5].png}
        \caption{$P(\theta_{5} | \alpha)$ - \Acs{Adadelta}}
        \label{fig:results:case_study:iris:p_theta:5}
    \end{subfigure}
    \par\medskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[6].png}
        \caption{$P(\theta_{6} | \alpha)$ - \Acs{Adam}}
        \label{fig:results:case_study:iris:p_theta:6}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[7].png}
        \caption{$P(\theta_{7} | \alpha)$ - \Acs{PSO}}
        \label{fig:results:case_study:iris:p_theta:7}
    \end{subfigure}
    \par\medskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[8].png}
        \caption{$P(\theta_{8} | \alpha)$ - \Acs{GA}}
        \label{fig:results:case_study:iris:p_theta:8}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/theta[9].png}
        \caption{$P(\theta_{9} | \alpha)$ - \Acs{DE}}
        \label{fig:results:case_study:iris:p_theta:9}
    \end{subfigure}
    \par\medskip
	\caption{Change in the sampled selection probability of $\theta$ during training for various heuristics}
	\label{fig:results:case_study:iris:p_theta}
\end{figure}

@@

\begin{figure}[htbp]
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[0].png}
        \caption{$P\left(h_{0} | \theta \right)$ - \Acs{SGD}}
        \label{fig:results:case_study:iris:p_H:0}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[1].png}
        \caption{$P\left(h_{1} | \theta \right)$ - \Acs{Momentum}}
        \label{fig:results:case_study:iris:p_H:1}
    \end{subfigure}
    \par\medskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[2].png}
		\caption{$P\left(h_{2} | \theta \right)$ - \Acs{NAG}}
		\label{fig:results:case_study:iris:p_H:2}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[3].png}
		\caption{$P\left(h_{3} | \theta \right)$ - \Acs{Adagrad}}
		\label{fig:results:case_study:iris:p_H:3}
	\end{subfigure}
	\par\medskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[4].png}
		\caption{$P\left(h_{4} | \theta \right)$ - \Acs{RMSProp}}
		\label{fig:results:case_study:iris:p_H:4}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[5].png}
		\caption{$P\left(h_{5} | \theta \right)$ - \Acs{Adadelta}}
		\label{fig:results:case_study:iris:p_H:5}
	\end{subfigure}
	\par\medskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[6].png}
		\caption{$P\left(h_{6} | \theta \right)$ - \Acs{Adam}}
		\label{fig:results:case_study:iris:p_H:6}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[7].png}
		\caption{$P\left(h_{7} | \theta \right)$ - \Acs{PSO}}
		\label{fig:results:case_study:iris:p_H:7}
	\end{subfigure}
	\par\medskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[8].png}
		\caption{$P\left(h_{8} | \theta \right)$ - \Acs{GA}}
		\label{fig:results:case_study:iris:p_H:8}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_H[9].png}
		\caption{$P\left(h_{9} | \theta \right)$ - \Acs{DE}}
		\label{fig:results:case_study:iris:p_H:9}
	\end{subfigure}
	\par\medskip
	\caption{Change in the prior heuristic selection probability $P\left(H\right | \theta )$ as the \Ac{BHH} learns during training}
	\label{fig:results:case_study:iris:p_H}
\end{figure}

@@

\begin{figure}[htbp]
    \begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/no_learning_theta.png}
        \caption{$P(\theta_{6} | \alpha)$}
        \label{fig:results:case_study:iris:no_learn:p_theta}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
    	\centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/no_learning_test_loss.png}
        \caption{Test loss}
        \label{fig:results:case_study:iris:no_learn:test:loss}
    \end{subfigure}
    \par\bigskip
    \caption{Comparing baseline \Acp{BHH} to that of a \Ac{BHH} with pure random selection.}
    \label{fig:results:case_study:iris:no_learn:metrics}
\end{figure}

@@

\begin{figure}[htbp]
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_HgEC[0][6].png}
        \caption{$P\left(h_{6}|e_{0},c_{1}\right)$ - entity 0 + \Acs{Adam} }
        \label{fig:results:case_study:iris:p_HgEC:0:6}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_HgEC[1][6].png}
        \caption{$P\left(h_{6}|e_{1},c_{1}\right)$ - entity 1 + \Acs{Adam} }
        \label{fig:results:case_study:iris:p_HgEC:1:6}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_HgEC[2][6].png}
        \caption{$P\left(h_{6}|e_{2},c_{1}\right)$ - entity 2 + \Acs{Adam} }
        \label{fig:results:case_study:iris:p_HgEC:2:6}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/p_HgEC[3][6].png}
        \caption{$P\left(h_{6}|e_{3},c_{1}\right)$ - entity 3 + \Acs{Adam} }
        \label{fig:results:case_study:iris:p_HgEC:3:6}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.5\textwidth]{analysis/bhh_case_study/iris/p_HgEC[4][6].png}
        \caption{$P\left(h_{6}|e_{4},c_{1}\right)$ - entity 4 + \Acs{Adam} }
        \label{fig:results:case_study:iris:p_HgEC:4:6}
    \end{subfigure}
    \par\bigskip
    \caption{Change in the realised output of the predictive model $P\left(H|E,C;\theta,\phi,\psi \right)$ showcasing the selection of the \Acs{Adam} optimiser/low-level heuristic as an example}
    \label{fig:results:case_study:iris:p_HgEC}
\end{figure}

@@

\begin{figure}[htbp]
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/HgEC[0].png}
        \caption{HgEC\lbrack0\rbrack - entity 0}
        \label{fig:results:case_study:iris:HgEC:0}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/HgEC[1].png}
        \caption{HgEC\lbrack1\rbrack - entity 1}
        \label{fig:results:case_study:iris:HgEC:1}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/HgEC[2].png}
        \caption{HgEC\lbrack2\rbrack - entity 2}
        \label{fig:results:case_study:iris:HgEC:2}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{analysis/bhh_case_study/iris/HgEC[3].png}
        \caption{HgEC\lbrack3\rbrack - entity 3}
        \label{fig:results:case_study:iris:HgEC:3}
    \end{subfigure}
    \par\bigskip
    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.5\textwidth]{analysis/bhh_case_study/iris/HgEC[4].png}
        \caption{HgEC\lbrack4\rbrack - entity 4}
        \label{fig:results:case_study:iris:HgEC:4}
    \end{subfigure}
    \par\bigskip
    \caption{Change in selected heuristics (HgEC) during training for various entities}
    \label{fig:results:case_study:iris:HgEC}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/standalone/figures/descriptive/descriptive.png}
	\caption{Descriptive plots between the average ranks of standalone heuristics compared to the baseline \Acs{BHH} per dataset, across all runs and steps.}
	\label{fig:results:standalone:descriptive:descriptive}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/standalone/figures/cd/overall.png}
	\caption{Critical difference plots between the average ranks of standalone heuristics compared to the baseline \Acs{BHH}, across all datasets, runs and steps.}
	\label{fig:results:standalone:descriptive:cd}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{analysis/bhh_heuristic_pool/figures/descriptive/descriptive.png}
	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying heuristic pools per dataset, across all runs and steps.}
	\label{fig:results:heuristic_pool:descriptive:descriptive}
\end{figure}

>>>>

\begin{figure}[htbp]
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/train_loss.png}
		\caption{Train loss}
		\label{fig:results:case_study:iris:train:loss}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/test_loss.png}
		\caption{Test loss}
		\label{fig:results:case_study:iris:test:loss}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/train_accuracy.png}
		\caption{Train accuracy}
		\label{fig:results:case_study:iris:train:accuracy}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/test_accuracy.png}
		\caption{Test accuracy}
		\label{fig:results:case_study:iris:test:accuracy}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[width=0.35\textwidth]{bhh_case_study/iris/legend.png}
		\caption{Legend}
		\label{fig:results:case_study:iris:legend}
	\end{subfigure}
	\par\bigskip
	\caption{Train and test behaviour of the \Ac{BHH} baseline for different configurations of replay window size}
	\label{fig:results:case_study:iris:metric_plots}
\end{figure}

@@

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[0].png}
		\caption{$\alpha_{0}$ - \Acs{SGD}}
		\label{fig:results:case_study:iris:alpha:0}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[1].png}
		\caption{$\alpha_{1}$ - \Acs{Momentum}}
		\label{fig:results:case_study:iris:alpha:1}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[2].png}
		\caption{$\alpha_{2}$ - \Acs{NAG}}
		\label{fig:results:case_study:iris:alpha:2}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[3].png}
		\caption{$\alpha_{3}$ - \Acs{Adagrad}}
		\label{fig:results:case_study:iris:alpha:3}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[4].png}
		\caption{$\alpha_{4}$ - \Acs{RMSProp}}
		\label{fig:results:case_study:iris:alpha:4}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[5].png}
		\caption{$\alpha_{5}$ - \Acs{Adadelta}}
		\label{fig:results:case_study:iris:alpha:5}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[6].png}
		\caption{$\alpha_{6}$ - \Acs{Adam}}
		\label{fig:results:case_study:iris:alpha:6}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[7].png}
		\caption{$\alpha_{7}$ - \Acs{PSO}}
		\label{fig:results:case_study:iris:alpha:7}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[8].png}
		\caption{$\alpha_{8}$ - \Acs{GA}}
		\label{fig:results:case_study:iris:alpha:8}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/alpha[9].png}
		\caption{$\alpha_{9}$ - \Acs{DE}}
		\label{fig:results:case_study:iris:alpha:9}
	\end{subfigure}
	\par\bigskip
	\caption{Change in the concentration of $\alpha$ during training for various heuristics}
	\label{fig:results:case_study:iris:alpha}
\end{figure}

@@

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[0].png}
		\caption{$P(\theta_{0} | \alpha)$ - \Acs{SGD}}
		\label{fig:results:case_study:iris:p_theta:0}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[1].png}
		\caption{$P(\theta_{1} | \alpha)$ - \Acs{Momentum}}
		\label{fig:results:case_study:iris:p_theta:1}
	\end{subfigure}
	\par\medskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[2].png}
		\caption{$P(\theta_{2} | \alpha)$ - \Acs{NAG}}
		\label{fig:results:case_study:iris:p_theta:2}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[3].png}
		\caption{$P(\theta_{3} | \alpha)$ - \Acs{Adagrad}}
		\label{fig:results:case_study:iris:p_theta:3}
	\end{subfigure}
	\par\medskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[4].png}
		\caption{$P(\theta_{4} | \alpha)$ - \Acs{RMSProp}}
		\label{fig:results:case_study:iris:p_theta:4}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[5].png}
		\caption{$P(\theta_{5} | \alpha)$ - \Acs{Adadelta}}
		\label{fig:results:case_study:iris:p_theta:5}
	\end{subfigure}
	\par\medskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[6].png}
		\caption{$P(\theta_{6} | \alpha)$ - \Acs{Adam}}
		\label{fig:results:case_study:iris:p_theta:6}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[7].png}
		\caption{$P(\theta_{7} | \alpha)$ - \Acs{PSO}}
		\label{fig:results:case_study:iris:p_theta:7}
	\end{subfigure}
	\par\medskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[8].png}
		\caption{$P(\theta_{8} | \alpha)$ - \Acs{GA}}
		\label{fig:results:case_study:iris:p_theta:8}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/theta[9].png}
		\caption{$P(\theta_{9} | \alpha)$ - \Acs{DE}}
		\label{fig:results:case_study:iris:p_theta:9}
	\end{subfigure}
	\par\medskip
	\caption{Change in the sampled selection probability of $\theta$ during training for various heuristics}
	\label{fig:results:case_study:iris:p_theta}
\end{figure}

@@

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[0].png}
		\caption{$P\left(h_{0} | \theta \right)$ - \Acs{SGD}}
		\label{fig:results:case_study:iris:p_H:0}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[1].png}
		\caption{$P\left(h_{1} | \theta \right)$ - \Acs{Momentum}}
		\label{fig:results:case_study:iris:p_H:1}
	\end{subfigure}
	\par\medskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[2].png}
		\caption{$P\left(h_{2} | \theta \right)$ - \Acs{NAG}}
		\label{fig:results:case_study:iris:p_H:2}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[3].png}
		\caption{$P\left(h_{3} | \theta \right)$ - \Acs{Adagrad}}
		\label{fig:results:case_study:iris:p_H:3}
	\end{subfigure}
	\par\medskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[4].png}
		\caption{$P\left(h_{4} | \theta \right)$ - \Acs{RMSProp}}
		\label{fig:results:case_study:iris:p_H:4}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[5].png}
		\caption{$P\left(h_{5} | \theta \right)$ - \Acs{Adadelta}}
		\label{fig:results:case_study:iris:p_H:5}
	\end{subfigure}
	\par\medskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[6].png}
		\caption{$P\left(h_{6} | \theta \right)$ - \Acs{Adam}}
		\label{fig:results:case_study:iris:p_H:6}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[7].png}
		\caption{$P\left(h_{7} | \theta \right)$ - \Acs{PSO}}
		\label{fig:results:case_study:iris:p_H:7}
	\end{subfigure}
	\par\medskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[8].png}
		\caption{$P\left(h_{8} | \theta \right)$ - \Acs{GA}}
		\label{fig:results:case_study:iris:p_H:8}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_H[9].png}
		\caption{$P\left(h_{9} | \theta \right)$ - \Acs{DE}}
		\label{fig:results:case_study:iris:p_H:9}
	\end{subfigure}
	\par\medskip
	\caption{Change in the prior heuristic selection probability $P\left(H\right | \theta )$ as the \Ac{BHH} learns during training}
	\label{fig:results:case_study:iris:p_H}
\end{figure}

@@

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/no_learning_theta.png}
		\caption{$P(\theta_{6} | \alpha)$}
		\label{fig:results:case_study:iris:no_learn:p_theta}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/no_learning_test_loss.png}
		\caption{Test loss}
		\label{fig:results:case_study:iris:no_learn:test:loss}
	\end{subfigure}
	\par\bigskip
	\caption{Comparing baseline \Acp{BHH} to that of a \Ac{BHH} with pure random selection.}
	\label{fig:results:case_study:iris:no_learn:metrics}
\end{figure}

@@

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_HgEC[0][6].png}
		\caption{$P\left(h_{6}|e_{0},c_{1}\right)$ - entity 0 + \Acs{Adam} }
		\label{fig:results:case_study:iris:p_HgEC:0:6}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_HgEC[1][6].png}
		\caption{$P\left(h_{6}|e_{1},c_{1}\right)$ - entity 1 + \Acs{Adam} }
		\label{fig:results:case_study:iris:p_HgEC:1:6}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_HgEC[2][6].png}
		\caption{$P\left(h_{6}|e_{2},c_{1}\right)$ - entity 2 + \Acs{Adam} }
		\label{fig:results:case_study:iris:p_HgEC:2:6}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/p_HgEC[3][6].png}
		\caption{$P\left(h_{6}|e_{3},c_{1}\right)$ - entity 3 + \Acs{Adam} }
		\label{fig:results:case_study:iris:p_HgEC:3:6}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[width=0.5\textwidth]{bhh_case_study/iris/p_HgEC[4][6].png}
		\caption{$P\left(h_{6}|e_{4},c_{1}\right)$ - entity 4 + \Acs{Adam} }
		\label{fig:results:case_study:iris:p_HgEC:4:6}
	\end{subfigure}
	\par\bigskip
	\caption{Change in the realised output of the predictive model $P\left(H|E,C;\theta,\phi,\psi \right)$ showcasing the selection of the \Acs{Adam} optimiser/low-level heuristic as an example}
	\label{fig:results:case_study:iris:p_HgEC}
\end{figure}

@@

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/HgEC[0].png}
		\caption{HgEC\lbrack0\rbrack - entity 0}
		\label{fig:results:case_study:iris:HgEC:0}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/HgEC[1].png}
		\caption{HgEC\lbrack1\rbrack - entity 1}
		\label{fig:results:case_study:iris:HgEC:1}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/HgEC[2].png}
		\caption{HgEC\lbrack2\rbrack - entity 2}
		\label{fig:results:case_study:iris:HgEC:2}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_case_study/iris/HgEC[3].png}
		\caption{HgEC\lbrack3\rbrack - entity 3}
		\label{fig:results:case_study:iris:HgEC:3}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{\textwidth}
		\centering
		\includegraphics[width=0.5\textwidth]{bhh_case_study/iris/HgEC[4].png}
		\caption{HgEC\lbrack4\rbrack - entity 4}
		\label{fig:results:case_study:iris:HgEC:4}
	\end{subfigure}
	\par\bigskip
	\caption{Change in selected heuristics (HgEC) during training for various entities}
	\label{fig:results:case_study:iris:HgEC}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.png}
	\caption{Descriptive plots between the average ranks of standalone heuristics compared to the baseline \Acs{BHH} per dataset, across all runs and steps.}
	\label{fig:results:standalone:descriptive:descriptive}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{standalone/figures/cd/overall.pdf}
	\caption{Critical difference plots between the average ranks of standalone heuristics compared to the baseline \Acs{BHH}, across all datasets, runs and steps.}
	\label{fig:results:standalone:descriptive:cd}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{bhh_heuristic_pool/figures/descriptive/descriptive.png}
	\caption{Descriptive plots between the average ranks of \Acsp{BHH} with varying heuristic pools per dataset, across all runs and steps.}
	\label{fig:results:heuristic_pool:descriptive:descriptive}
\end{figure}
